---
title: "R_Assignment_3"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## import 
```{r}
library(vroom)
library(haven)
library(tidyverse)
library(lubridate)
library(lme4)
library(plyr)
gc()
```

## import data
```{r}
dsf = vroom('dsf.csv') %>% glimpse()
```
## 2. Summarise
```{r}
report_stat_dsf <- dsf %>%
  select(-DATE, -HSICCD)  %>%
  summarise_all(list(function(x)mean(x,na.rm= T), function(x)sd(x,na.rm= T), function(x)quantile(x, .25,na.rm= T), function(x)quantile(x, .50,na.rm= T), function(x)quantile(x, .75,na.rm= T))) %>% 
  gather(key='var_name', value="value") %>%
  spread(key='var_name', value='value') %>%
  rename_at(vars(ends_with("fn1")), funs(str_replace(., "fn1", "mean")))%>%
  rename_at(vars(ends_with("fn2")), funs(str_replace(., "fn2", "std")))%>%
  rename_at(vars(ends_with("fn3")), funs(str_replace(., "fn3", "p25")))%>%
  rename_at(vars(ends_with("fn4")), funs(str_replace(., "fn4", "p50")))%>%
  rename_at(vars(ends_with("fn5")), funs(str_replace(., "fn5", "p75")))%>%
  glimpse()
```

## 3. (a) Compute average return over time
```{r}

report_daily_stat_dsf <- dsf %>%
  select(-HSICCD) %>%
  group_by(DATE)  %>%
  summarise_all(list(function(x)mean(x,na.rm= T), function(x)sd(x,na.rm= T), function(x)quantile(x, .25,na.rm= T), function(x)quantile(x, .50,na.rm= T), function(x)quantile(x, .75,na.rm= T))) %>% 
  gather(-DATE, key='var_name', value="value") %>%
  spread(key='var_name', value='value') %>%
  rename_at(vars(ends_with("fn1")), funs(str_replace(., "fn1", "mean")))%>%
  rename_at(vars(ends_with("fn2")), funs(str_replace(., "fn2", "std")))%>%
  rename_at(vars(ends_with("fn3")), funs(str_replace(., "fn3", "p25")))%>%
  rename_at(vars(ends_with("fn4")), funs(str_replace(., "fn4", "p50")))%>%
  rename_at(vars(ends_with("fn5")), funs(str_replace(., "fn5", "p75")))%>%
  glimpse()
```

## 3. (b) Compute average return over time

- From the daily mean spread, we can see a trend of increasing
- From the volume standard deviation, we can see a rise near 2008
- Price mean have a large drop in 2008, Price p25 even has a larger drop

```{r}
report_daily_stat_dsf = report_daily_stat_dsf %>% mutate(date=dmy(DATE)) %>% na.omit()%>%glimpse() 
for (name in colnames(report_daily_stat_dsf)[2:21])   
  {   
    print(ggplot(data = report_daily_stat_dsf, aes_string(x="date", y = name)) + geom_line())
  } 
```

## 4. Regression CAPM
### Import market return data 
```{r}

dsi = read_sas('dsi.sas7bdat') %>% 
  filter(date > ymd("2003-12-31")) %>%
  filter(date < ymd("2019-01-01")) %>%
  glimpse()

dsf_rmt = dsf %>% mutate(date=dmy(DATE)) %>% select(-DATE) %>% merge(dsi, by="date")
dsf_rmt %>% glimpse()
```

## Reg over all the security

```{r}
dsf = NULL
gc()

reg_results = lmList(RET ~ EWRETX | HSICCD, data=dsf_rmt)

reg_results %>% glimpse()
reg_results[1] %>% glimpse()
```

## Calculate Volitility
```{r}

get_vol <- function(reg){
  model = reg$model
  coef = reg$coefficients
  total_vol = sd(model$RET, na.rm = TRUE)
  system_vol = sd(coef["EWRETX"] * model$EWRETX, na.rm=TRUE)
  idio_vol = sd(reg$residuals, na.rm=TRUE)
  l = list()
  l['system_vol'] = system_vol
  l['total_vol'] = total_vol
  l['idio_vol'] = idio_vol
  l
}


vol_results =  lapply(reg_results, get_vol)
```

## 3(d) sort by system vol and calculate performance


```{r}
vol_df <- ldply (vol_results, data.frame) %>% rename(c('.id' = 'HSICCD')) %>% mutate(HSICCD = as.double(HSICCD))  %>% glimpse()

system_vol_df <- vol_df %>% arrange(system_vol) %>% glimpse()

top_q20 = system_vol_df %>% slice(1:(918 / 5)) %>% glimpse()
tail_q20 = system_vol_df %>% slice((918 * 0.8):918) %>% glimpse()

system_vol_portfolio_ret = dsf_rmt %>% 
  select(RET, date, HSICCD) %>%
  merge(top_q20, by="HSICCD") %>%
  group_by(date) %>% 
  summarise_at(vars(RET), funs(mean(., na.rm=TRUE))) %>%
  merge(dsf_rmt %>% 
      select(RET, date, HSICCD) %>%
      merge(tail_q20, by="HSICCD") %>%
      group_by(date) %>% 
      summarise_at(vars(RET), funs(mean(., na.rm=TRUE))), by="date") %>%
  glimpse()

system_vol_portfolio_ret %>%
  mutate(port_ret = RET.x - RET.y) %>%
  summarise_at(vars(port_ret), funs(mean(., na.rm=TRUE), sd(., na.rm=TRUE))) %>%
  glimpse()
```
- The quintile porfolio (sorting over systematic volitility)'s return is shown above  
- When the quintile porfolio is formed by sorting over systematic volitility we have mean daily return of 0.00038
- That means we have a averagely positive return every day.


## 3(e) sort by idio vol and calculate performance
```{r}
idio_vol_df <- vol_df %>% arrange(idio_vol) %>% glimpse()

top_q20 = idio_vol_df %>% slice(1:(918 / 5)) %>% glimpse()
tail_q20 = idio_vol_df %>% slice((918 * 0.8):918) %>% glimpse()

idio_vol_portfolio_ret = dsf_rmt %>% 
  select(RET, date, HSICCD) %>%
  merge(top_q20, by="HSICCD") %>%
  group_by(date) %>% 
  summarise_at(vars(RET), funs(mean(., na.rm=TRUE))) %>%
  merge(dsf_rmt %>% 
      select(RET, date, HSICCD) %>%
      merge(tail_q20, by="HSICCD") %>%
      group_by(date) %>% 
      summarise_at(vars(RET), funs(mean(., na.rm=TRUE))), by="date") %>%
  glimpse()

idio_vol_portfolio_ret %>%
  mutate(port_ret = RET.x - RET.y) %>%
  summarise_at(vars(port_ret), funs(mean(., na.rm=TRUE), sd(., na.rm=TRUE))) %>%
  glimpse()
```
- The quintile porfolio (sorting over idiosyncracy volitility)'s return is shown above  
- When the quintile porfolio is formed by sorting over idiosyncracy volitility we have mean daily return of -0.00023
- That means we have a averagely negative return every day.

## Summary
- From the decomposition of total volitility by systematic volility and idiosyncracy volitility
- Systematic votility is smaller than idiosyncracy volitility in magnitudes.
- The performances of systematic volitility sorted quintile porfolio is better
- It is probably because the systematic trend of increasing since 2008
- It is consistent with the trend of rising of passive investment, which capture more in systematic volitility

